A Unification of Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-14 colt-21/cvx-flats.tex
Working on results in Section 4

\newcommand{\range}{\mathrm{range}\,}
\newcommand{\zeros}[1]{\mathrm{ker}_\P\,#1}
\newcommand{\codim}{\mathrm{codim}}
\newcommand{\Pcodim}{\mathcal{P}\!\text{-}\mathrm{codim}}
\newcommand{\Pcodimension}{$\mathcal{P}$-codimension}

@@

If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
We write $\L_d^{inf} $\jessie{Add conditions on $\L$ for infinite $\Y$} for the set of minimizable, $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$; we will use this class of loss functions with $\Y$ such that $|\Y| = \infty$ in mind. \jessie{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
Moreover, we write $\L_d = \L_d^{inf} \cup \L_d^{fin}$ and $\L = \cup_{d \in \N} \L_d$.
%We write $\L_d = \L_d^{inf} \cup \L_d^{fin}$\jessie{Add conditions on $\L$ for infinite $\Y$} for the set of surrogates $L: \reals^d \times \Y \to \reals$ that are always minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\simplex$, and write $\L = \cup_{d \in \mathbb{N}} \L_d$.
A loss $\ell$ is \emph{discrete} if $\R$ is a finite set.
A surrogate $L$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ for every label $y \in \Y$.
For a given $p\in\simplex$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
Typically, we notate finite report sets $\R$ (and $\R'$ if a second finite set is needed) and continuous prediction spaces $\U \subseteq \reals^d$.

@@

Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
Moreover, $\ker(W) = \{p \in \simplex : Wp = \vec 0\}$ is the kernel of matrix $W$.
%Recall that the affine hull is the set of all linear combinations whose coefficients sum to 1.
%In particular, we will often use \footnote{Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.}\jessiet{Space suggestion: move terse version of this to footnote.}
\begin{definition}[Flat]\label{def:flat}
	A \emph{flat} $F \subseteq \affhull(\simplex)$ $\subseteq \reals^n$ is a nonempty set $F = \ker W \cap \affhull(\simplex)$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
	The codimension of $F$ is given by $\codim(F)=\mathrm{rank}(W)$, and the dimension of $F$ (relative to $\affhull(\simplex)$) is $n - \mathrm{rank}(W) - 1$.
\end{definition}

\jessie{Aiming for a unified definition here}
\begin{definition}[\jessie{Unified definition: }Flat]\label{def:flat-general}
	A \emph{flat} $F \subseteq \P$ $\subseteq \reals^n$ is a nonempty set $F = \ker_\P(W) = \{p \in \P : \E_p W = \vec 0\}$ for some $W:\Y \to \reals^d$.
	Furthermore, we define $\codim(F) := \dim(\spn(\P) / \spn(F))$.

	%recover this later
	If $n$ is finite, the codimension of $F$ is given by $\codim(F)=\mathrm{rank}(W)$.
	If $n$ is infinite, consider $\codim(F) = \dim(\{p + F : p \in \P\}) \leq d$.
\end{definition}
\jessie{There's a bit of nuance about $W$ being a matrix vs function}

@@

\begin{definition}[\Pcodimension]
	The \emph{\Pcodimension} of a convex set $F \subseteq \P$ is the minimum $d$ such that there exists a measurable function $V : \Y \to \reals^d$ such that $F = \zeros{V}$, and is denoted $\Pcodim(F)$.
\end{definition}

\begin{lemma}
	  \label{thm:convex-flats-inf-dim}\jessie{Edit to be about $\Gamma$}
	Let $\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$.
	For all $u\in\range\Gamma$ and $p\in\Gamma_r$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_r$.
\end{lemma}
\begin{proof}
	\jessie{Direct}
		Let $\Gamma := \prop{L}$.
		As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
		We proceed in two cases, depending on $|\Y|$.

@@

		\emph{Infinite $\Y$: }	
		$L \in \L^{inf}_d$ implies $L$ satisfies the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we can interchange subdifferentiation and expectation to observe $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y) := \cl\{\int V(y)dp(y) : V \mathrm{msbl}, V(y) \in \partial L(u,y) a.s.\}$.
		We can now take $V_{u,p}$ to be such a $V: \Y \to \reals^d$, which exists as the subgradient is nonempty.

		In both cases, we take the flat $F := \zeros{V_{u,p}}$, and have $\codim(F) \leq d$ by Definition~\ref{def:flat}, and $p \in F$ by construction. \jessie{Flesh out}
		To see $F \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\P$ that $q \in \zeros{V_{u,p}} \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
\end{proof}

\begin{lemma}
	Let $\gamma$ be indirectly elicited by some $\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$.
	For all $r\in\range\gamma$ and $p$ such that $|\gamma(p)| = 1$ with $\{r\} = \gamma(p)$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{\hat V_{u,p}} \subseteq \gamma_r$.
\end{lemma}

\begin{lemma}
	Let $\gamma$ be indirectly elicited by some $\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$, and suppose $\gamma$ is elicitable on $\P$ defined over finite $\Y$.
	For all $r\in\range\gamma$ and $p \in \relint{\P}$ such that $p \in \gamma_r$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \gamma_r$.
\end{lemma}

\begin{corollary} \jessie{Indirect}
	Given target property $\gamma:\P \to\to \reals^d$, if there is some $p \in \P$ such that $|\gamma(p)| = 1$ with $\gamma(p) = \{r\}$, and there is not a flat $\zeros{\hat V_{u,p}} \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\hat \Gamma$.
\end{corollary}

\begin{corollary} \jessie{Indirect}
	Given target property $\gamma:\P \to\to \reals^d$, where $\P$ is defined over a finite set of outcomes $\Y$, if there is some $p \in \relint{\P}$ and there is not a flat $\zeros{\hat V_{u,p}} \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
\end{corollary}

\begin{theorem}\label{thm:cvx-flats}
  Let a property $\gamma:\simplex\toto\R$ be given, let $p\in\simplex$ such that either (i) $|\gamma(p)|=1$ or (ii) $\gamma$ is elicitable and $p\in\relint\simplex$, and let $r\in\gamma(p)$.
Then if a convex $L: \reals^d \times \Y \to \reals$ \jessie{in $\L_d$} indirectly elicits $\gamma$, there is a flat $F$ with $p\in F \cap \simplex \subseteq \gamma_r$ and $\codim(F) \leq d$.
% COmmented 06.03.20
%	If there is a convex surrogate loss $L : \reals^d \times\Y \to \reals$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
\end{theorem}
\begin{proof}

@@

The main known technique for lower bounds on surrogate dimensions is given by \citet{ramaswamy2016convex} for the quadrant of a target loss and discrete predictions.
The proof heavily builds around the ``limits of sequences'' in the definition of calibration.
By restricting slightly to the broad class of minimizable losses $\L$, we show their bound follows relatively directly from Theorem \ref{thm:cvx-flats}.
(We conjecture that the restriction to $\L$ can be lifted; see \S~\ref{sec:conclusions}.)
% \footnote{We conjecture, as an intriguing open problem, that even this restriction can be lifted and the bound of \citet{ramaswamy2016convex} can be entirely recovered via indirect elicitation lower bounds; perhaps by generalizing the definition of indirect elicitation to apply to non-minimizable losses in some way.}
%\citet{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now. \bo{Ideally we've explained the connection earlier and don't need to say it here.}}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
\citet{ramaswamy2016convex} construct what they call the subspace of feasible dimensions and give bounds in terms of its dimension.
\begin{definition}[Subspace of feasible directions]\label{def:subspace-feas}
	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at $p \in \C$ is $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
\end{definition}

@@

\begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
	Let $\ell:\R \to \reals^\Y_+$ be a discrete loss eliciting $\gamma$, and let $L \in \L_d$ be a minimizable consistent convex surrogate for $\ell$.
	Then for all $p \in \simplex$ and $r \in \gamma(p)$,
	\begin{equation}
	  d \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
	\end{equation}
%% Bo: old version, Jun 4 7pm
%%	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
%%	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
%%	\begin{equation}
%%	\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
%%	\end{equation}\jessiet{TODO: add minnability\bo{Tried!}}
\end{restatable}
\begin{proof}[Proof sketch]
	%\btw{Bo: rearranged the statements here a little, I felt the previous version required the reader to keep a bit more in their head.}
	First, take $p \in \relint{\simplex}$ for intuition.
	Theorem~\ref{thm:cvx-flats} guarantees the existence of a flat $F$ of dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$.
	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq F - p$.
	This yields $\dim(\Sc_{\gamma_r}(p)) \geq n - d - 1$, completing the proof for $p \in \relint{\simplex}$.

>>>>

\newcommand{\range}{\mathrm{range}\,}
\newcommand{\zeros}[1]{\mathrm{ker}_\P\,#1}
\newcommand{\codim}{\mathrm{codim}}
\newcommand{\Pcodim}{\mathcal{P}\!\text{-}\mathrm{codim}}
\newcommand{\Pcodimension}{$\mathcal{P}$-codimension\,}

@@

If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
We write $\L_d^{inf} $\jessie{Add conditions on $\L$ for infinite $\Y$} for the set of minimizable, $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$; we will use this class of loss functions with $\Y$ such that $|\Y| = \infty$ in mind. \jessie{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
Moreover, we write $\L_d = \L_d^{inf} \cap \L_d^{fin}$ and $\L = \cup_{d \in \N} \L_d$.
%We write $\L_d = \L_d^{inf} \cup \L_d^{fin}$\jessie{Add conditions on $\L$ for infinite $\Y$} for the set of surrogates $L: \reals^d \times \Y \to \reals$ that are always minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\simplex$, and write $\L = \cup_{d \in \mathbb{N}} \L_d$.
A loss $\ell$ is \emph{discrete} if $\R$ is a finite set.
A surrogate $L$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ for every label $y \in \Y$.
For a given $p\in\simplex$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
Typically, we notate finite report sets $\R$ (and $\R'$ if a second finite set is needed) and continuous prediction spaces $\U \subseteq \reals^d$.

@@

Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
Moreover, $\ker(W) = \{p \in \simplex : Wp = \vec 0\}$ is the kernel of matrix $W$.
%Recall that the affine hull is the set of all linear combinations whose coefficients sum to 1.
%In particular, we will often use \footnote{Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.}\jessiet{Space suggestion: move terse version of this to footnote.}
\begin{definition}[Flat]\label{def:flat}\btw{Jessie: Suggest delete}
	A \emph{flat} $F \subseteq \affhull(\simplex)$ $\subseteq \reals^n$ is a nonempty set $F = \ker W \cap \affhull(\simplex)$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
	The codimension of $F$ is given by $\codim(F)=\mathrm{rank}(W)$, and the dimension of $F$ (relative to $\affhull(\simplex)$) is $n - \mathrm{rank}(W) - 1$.
\end{definition}

\jessie{Aiming for a unified definition here}
\begin{definition}[\jessie{Unified definition: }Flat]\label{def:flat-general}
	A \emph{flat} $F \subseteq \P$ $\subseteq \reals^n$ is a nonempty set $F = \ker_\P(W) = \{q \in \P : \E_q W = \vec 0\}$ for some $W:\Y \to \reals^d$.
	Furthermore, we define $\codim(F) := \dim(\spn(\P) / \spn(F))$.

	%recover this later
	\btw{Jessie: Suggest delete}
	If $n$ is finite, the codimension of $F$ is given by $\codim(F)=\mathrm{rank}(W)$.
	If $n$ is infinite, consider $\codim(F) = \dim(\{p + F : p \in \P\}) \leq d$.
\end{definition}
\jessie{There's a bit of nuance about $W$ being a matrix vs function}

@@

\begin{definition}[$\P$-codimension]
	The \emph{\Pcodimension} of a convex set $F \subseteq \P$ is the minimum $d$ such that there exists a measurable function $V : \Y \to \reals^d$ such that $F = \zeros{V}$, and is denoted $\Pcodim(F)$.
\end{definition}

\begin{lemma}
	  \label{thm:convex-flats-inf-dim}
	Let $\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$.
	For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
\end{lemma}
\begin{proof}
	\jessie{Direct}
		Let $\Gamma := \prop{L}$.
		As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
		We proceed in two cases, depending on $|\Y|$.

@@

		\emph{Infinite $\Y$: }	
		$L \in \L^{inf}_d$ and convex \jessie{Need to be explicit in our definition of $\C^*$ to imply $L \in \L^{inf}_d$} implies $L$ satisfies the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we can interchange subdifferentiation and expectation to observe $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y) := \cl\{\int V(y)dp(y) : V \mathrm{msbl}, V(y) \in \partial L(u,y) a.s.\}$.
		We can now take $V_{u,p}$ to be such a $V: \Y \to \reals^d$, which exists as the subgradient is nonempty.

		In both cases, we take the flat $F := \zeros{V_{u,p}}$, and have $p \in F$ by construction.
		To see $F \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\P$ that $q \in \zeros{V_{u,p}} \implies \vec 0 \in \partial \E_q L(u,Y) \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
\end{proof}

\begin{lemma}
	Let $\gamma$ be indirectly elicited by some $\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$.
	For all $r\in\range\gamma$ and $p$ such that $|\gamma(p)| = 1$ with $\{r\} = \gamma(p)$, there is some flat $F$ \jessie{of \Pcodimension at most $d$?} such that $p \in F \subseteq \gamma_r$.
\end{lemma}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{thm:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
	Thus, we have $p \in F \subseteq \gamma_r$.
\end{proof}

\begin{corollary} 
	Given target property $\gamma:\P \toto \reals^d$, if there is some $p \in \P$ such that $|\gamma(p)| = 1$ with $\gamma(p) = \{r\}$, and there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\hat \Gamma$.
\end{corollary}

\begin{lemma}
	Let $\gamma$ be indirectly elicited by some $\Gamma\in\C^*_d$ for some $d\in\mathbb{N}$, and suppose $\gamma$ is elicitable on $\P$ defined over finite $\Y$.
	For all $r\in\range\gamma$ and $p \in \relint{\P}$ such that $p \in \gamma_r$, there is some flat $F$ \jessie{of \Pcodimension at most $d$} such that $p \in F \subseteq \gamma_r$.
\end{lemma}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$, and suppose $r' = \psi(u)$.
	Take $F \subseteq \Gamma_u$ to be the flat that exists by Lemma~\ref{thm:convex-flats-inf-dim}.
	If $r = r'$, then $p \in F \subseteq \Gamma_u \subseteq \gamma_r$ by indirect elicitation.
	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.
\end{proof}

\begin{corollary} 
	Given target property $\gamma:\P \toto \reals^d$, where $\P$ is defined over a finite set of outcomes $\Y$, if there is some $p \in \relint{\P}$ and there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
\end{corollary}

\btw{Jessie: Suggest delete - this is the original version}
\begin{theorem}\label{thm:cvx-flats}
  Let a property $\gamma:\simplex\toto\R$ be given, let $p\in\simplex$ such that either (i) $|\gamma(p)|=1$ or (ii) $\gamma$ is elicitable and $p\in\relint\simplex$, and let $r\in\gamma(p)$.
Then if a convex $L: \reals^d \times \Y \to \reals$ \jessie{in $\L_d$} indirectly elicits $\gamma$, there is a flat $F$ with $p\in F \cap \simplex \subseteq \gamma_r$ and $\codim(F) \leq d$.
% COmmented 06.03.20
%	If there is a convex surrogate loss $L : \reals^d \times\Y \to \reals$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
\end{theorem}
\begin{proof}

@@

The main known technique for lower bounds on surrogate dimensions is given by \citet{ramaswamy2016convex} for the quadrant of a target loss and discrete predictions.
The proof heavily builds around the ``limits of sequences'' in the definition of calibration.
By restricting slightly to the broad class of minimizable losses $\L$ \jessie{$\L^{fin}$}, we show their bound follows relatively directly from Theorem \ref{thm:cvx-flats}.
(We conjecture that the restriction to $\L$ can be lifted; see \S~\ref{sec:conclusions}.)
% \footnote{We conjecture, as an intriguing open problem, that even this restriction can be lifted and the bound of \citet{ramaswamy2016convex} can be entirely recovered via indirect elicitation lower bounds; perhaps by generalizing the definition of indirect elicitation to apply to non-minimizable losses in some way.}
%\citet{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now. \bo{Ideally we've explained the connection earlier and don't need to say it here.}}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
\citet{ramaswamy2016convex} construct what they call the subspace of feasible dimensions and give bounds in terms of its dimension.
\begin{definition}[Subspace of feasible directions]\label{def:subspace-feas}
	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at $p \in \C$ is $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
\end{definition}

@@

\begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
	Let $\ell:\R \to \reals^\Y_+$ be a discrete loss eliciting $\gamma$, and let $L \in \L_d$ be a minimizable consistent convex surrogate for $\ell$.
	Then for all $p \in \simplex$ and $r \in \gamma(p)$,
	\begin{equation}
	  d \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
	\end{equation}
%% Bo: old version, Jun 4 7pm
%%	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
%%	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
%%	\begin{equation}
%%	\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
%%	\end{equation}\jessiet{TODO: add minnability\bo{Tried!}}
\end{restatable}
\begin{proof}[Proof sketch]
	%\btw{Bo: rearranged the statements here a little, I felt the previous version required the reader to keep a bit more in their head.}
	First, take $p \in \relint{\simplex}$ for intuition.
	Theorem~\ref{thm:cvx-flats} guarantees the existence of a flat $F$ of dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$. \jessie{Need to be careful to relate \Pcodimension to dimension}
	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq F - p$.
	This yields $\dim(\Sc_{\gamma_r}(p)) \geq n - d - 1$, completing the proof for $p \in \relint{\simplex}$.
